\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-10-07 paper.qmd
Changed the prop density calculation and added new notations to the table

## Find the minimum MSE when have duplicate a1
error_two_curvy_clust_umap <- error_two_curvy_clust_umap |>
  group_by(a1) |>
  filter(bin1 == min(bin1)) |>
  ungroup() |>
  mutate(prop_dens = b/side_length)

@@

>>>>

## Find the minimum MSE when have duplicate a1
error_two_curvy_clust_umap <- error_two_curvy_clust_umap |>
  group_by(a1) |>
  filter(bin1 == min(bin1)) |>
  ungroup() |>
  mutate(prop_dens = 1/(b*side_length^2))

@@

##### Density of a bin

Area of a hexagon is defined as $A = \frac{3\sqrt{3}}{2}l^2$ where $l$ is the side length of the hexagon. If we know $a_1$ and $a_2$, $l$ can be computed (see appendix). Therefore, the density of a hexagon grid is computed as $\frac{\sum^{h}_{i=1}n_h}{A}$ and the proportion is $\frac{\sum^{h}_{i=1}n_h}{A \times b}$. The base line proportion is defined as the

### 2024-10-07 paper.tex
Changed the prop density calculation and added new notations to the table

\begin{tabular}{>{\raggedright\arraybackslash}p{3cm}>{\raggedright\arraybackslash}p{12cm}}
\toprule
\textbf{Notation} & \textbf{Description}\\
\midrule
$n, p, k$ & number of observations, variables, embedding dimension, respectively\\
$\mathbfit{X}, \mathbfit{x}$ & $p$-dimensional data (population, sample)\\
$\mathbfit{y}$ & $k$-dimensional layout\\
$P$ & orthonormal basis, generating a $d\text{-}dimensional$ linear projection of $p$-dimensional data\\
$T$ & true  model\\
\addlinespace
$g$ & functional mapping from \pD{} to \kD{}, especially as prescribed by NLDR\\
$\mathbfit{\theta}$ & (Hyper-) parameters for NLDR method\\
$r$ & ranges of the embedding components\\
$C^{(j)}$ & $j$-dimensional bin centers\\
$(b_1, b_2)$ & number of bins in each direction\\
\addlinespace
$(a_1, a_2)$ & binwidths, distance between centroids in each direction\\
$(s_1, \ s_2)$ & starting coordinates of the hexagonal grid\\
$q$ & buffer to ensure hexgrid covers data, proportion of data range, 0-1\\
$m$ & number of non-empty bins\\
$b$ & number of  hexagons in the grid\\
\addlinespace
$h$ & hexagonal id\\
\bottomrule
\end{tabular}
\endgroup{}

@@

>>>>

\begin{tabular}{>{\raggedright\arraybackslash}p{3cm}>{\raggedright\arraybackslash}p{12cm}}
\toprule
\textbf{Notation} & \textbf{Description}\\
\midrule
$n, p, k$ & number of observations, variables, embedding dimension, respectively\\
$\mathbfit{X}, \mathbfit{x}$ & $p$-dimensional data (population, sample)\\
$\mathbfit{y}$ & $k$-dimensional layout\\
$P$ & orthonormal basis, generating a $d\text{-}dimensional$ linear projection of $p$-dimensional data\\
$T$ & true  model\\
\addlinespace
$g$ & functional mapping from \pD{} to \kD{}, especially as prescribed by NLDR\\
$\mathbfit{\theta}$ & (Hyper-) parameters for NLDR method\\
$r$ & ranges of the embedding components\\
$C^{(j)}$ & $j$-dimensional bin centers\\
$(b_1, b_2)$ & number of bins in each direction\\
\addlinespace
$(a_1, a_2)$ & binwidths, distance between centroids in each direction\\
$(s_1, \ s_2)$ & starting coordinates of the hexagonal grid\\
$q$ & buffer to ensure hexgrid covers data, proportion of data range, 0-1\\
$m$ & number of non-empty bins\\
$b$ & number of  hexagons in the grid\\
\addlinespace
$h$ & hexagonal id\\
$l$ & side length\\
$A$ & area\\
\bottomrule
\end{tabular}
\endgroup{}

@@

\paragraph{Density of a bin}\label{density-of-a-bin}

Area of a hexagon is defined as \(A = \frac{3\sqrt{3}}{2}l^2\) where
\(l\) is the side length of the hexagon. If we know \(a_1\) and \(a_2\),
\(l\) can be computed (see appendix). Therefore, the density of a
hexagon grid is computed as \(\frac{\sum^{h}_{i=1}n_h}{A}\) and the
proportion is \(\frac{\sum^{h}_{i=1}n_h}{A \times b}\). The base line
proportion is defined as the
